Alleviating Topology Mismatch in Distributed Overlay Networks: A Survey

### 2014-01-27 background.tex
2012.10.24 (Vassilis) Changed paper title. Text reworked (content clarifications added, typos corrected, broken references fixed).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Peer-to-Peer (P2P) Overlay Architectures}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Circa 2000, the first P2P file-sharing systems introduced the \emph{servent}
concept \cite{gnutella}, a \emph{portmanteau} that blends the notions of server
and client to denote the twofold role of a node participating in the P2P
network. Such serverless systems have proven to be able to achieve outstanding
aggregate resource capacities as more and more participants join the system
without requiring additional expenditure for infrastructure. While certain
undesirable features such as 
free-riding~\cite{saroiu_measurefileshare_2002,adar_gnutellafreeriders_2000,hughes_gnutellafreeride_2005},
the distribution of illegal content and other \emph{socio-technical}
issues \cite{hughes_socp2p_2008}, have arisen, peer-to-peer systems have
continued to gain popularity mainly because they have successfully supported
popular applications (i.e. file-sharing) amongst vast numbers of participating
users.

@@

Designers of \emph{centralized} architectures
(seeFigure~\ref{figure:p2p-archs:centralised}) were the first to recognise that
requests for resources (e.g. CPU cycles or popular content) need
not be sent to a dedicated server but instead could be handled by
the many hosts that already posess the resources. The downside of this approach
is that it requires a centralized searching facility which becomes a single
point of failure, a scalability bottleneck, and a target of malicious attacks
(e.g., \emph{Denial-of-Service (DoS) attacks}).

The most successful incarnation of the centralized approach is the file-sharing
application \emph{Napster}. % TODO find citation for Napster again \cite{}
Napster maintained a \emph{central index server} based on file lists provided by
participating peers. The central index server was queried by users and it
returned pointers to the actual content. Thus, by centralizing search while
distributing downloads, Napster achieved a highly functional design that, at its
height, attracted 26 million users sharing approximately 80 million
songs~\cite{jmm_naptopusage_2001}. Napster's centralized nature was ultimately
what brought it down after Recording Industry Association of America (RIAA) 
filed a lawsuit for copyright infringement of the intellectual property of
artists whose music was distributed by the Napster application. RIAA was able to
point to the centralized indexing component of Napster as the entity responsible
for illegal song-trading.

The centralized approach was quickly replaced by architectures that distribute
both search and resource provision capabilities (see
Figure~\ref{figure:p2p-archs:unstructured-full}). In these \emph{decentralized}
architectures, resource placement within the overlay topology is
random~\cite{YG-M2002}. For this reason they are referred to as
\emph{unstructured}. The most important properties of such systems are that they
support inherent heterogeneity of peers, are highly resilient to peer failures,
and incur low maintenance overhead at handling the dynamics of peer
participation \cite{stutzbach_churn_2006}. In the literature, they are also
known as \emph{broadcast-based} systems, because they use message flooding among
peers to propagate search queries. A well-known example of the fully dentralized
unstructured approach is Gnutella, in its first realisation (v.0.4)
\cite{gnutellav04}.

A key disadvantage of the unstructured approach is that message flooding burdens
the network since queries travel within the network randomly, visiting nodes
that do not have the resource of interest and thus wasting bandwidth.  To save
on bandwidth, unstructured networks typically limit how long a query travels
within the overlay (via a time-to-live (TTL) parameter). When a query is
received by a node, it decreases the TTL by one unit. If the TTL has not reached
zero, the node forwards the query to its neighbours.  Otherwise, it drops the
query. While this approach prevents queries from visiting the entire network, it
does not guarantee that the resource of interest, (e.g., a rare recording 
of a musical group from the 1930s) will be found.

@@

To fully address the disadvantages of decentralized unstructured approaches,
\emph{decentralized structured} schemes have been proposed (see
Figure~\ref{figure:p2p-archs:structured}). The key goal of these systems is to
provide a self-organising infrastructure for large-scale P2P applications
\cite{ratnasamy_can_2001,stoica_chord_2001,antony_pastry_2001,zhao_tapestry_2001,maymounkov_kademlia_2002,rgrk_bamboo_2004}.
They implement a \emph{Distributed Hash Table (DHT)} that maps objects to nodes
through a deterministic mechanism. The DHT provides a guaranteed bound on the
number of overlay routing hops that have to be taken to locate a resource, even
in the case when only a single copy exists in the system.  This means
$O \left( log n \right)$ hops, compared to unstructured networks that require
$O \left( n \right)$ to reliably locate any object. Unfortunately this
efficiency does not come without cost. Structured overlays can only support
exact-match queries (i.e., queries that identify resources by name) as opposed
to content-based retrieval provided by unstructured overlays. This means
that unstructured overlays can support more versatile resource location queries
such as keyword and partial matching searches. Several popular file-sharing
peer-to-peer applications have been based on DHTs including
Overnet/eDonkey~\cite{overnet}, Kademlia/Kad
Network~\cite{maymounkov_kademlia_2002}, some flavors of
BitTorrent~\cite{c_bittorrent_2003}, and many more.  Moreover, DHTs have sparked
a flurry of research activity and development for a large range of applications:
from distributed search engines to event notification infrastructures to
cloud-based platforms.We cite several examples in the Introduction.

% TODO: Change these pictures to match look-n-feel
\begin{figure}[ht]
\centering
\subfigure[Centralised (SETI@Home or Napster).] {
  \includegraphics[scale=0.25]{img/pdf/centralised.pdf}
  \label{figure:p2p-archs:centralised}
}\qquad\qquad
\subfigure[Fully unstructured (Gnutella v.0.4).] {
  \includegraphics[scale=0.25]{img/pdf/unstructured-full.pdf}
  \label{figure:p2p-archs:unstructred-full}
}\qquad\qquad
\subfigure[Hierarchical unstructured (Gnutella v.0.6 or FastTrack).] {
  \includegraphics[scale=0.25]{img/pdf/unstructured-hierarchical.pdf}
  \label{figure:p2p-archs:unstructured-hierarchical}
}\qquad\qquad
\subfigure[Structured (Chord and Kademlia).] {
  \includegraphics[scale=0.25]{img/pdf/structured.pdf}
  \label{figure:p2p-archs:structured}
}
\caption{The various peer-to-peer architectures.}
\label{figure:p2p-archs}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% TODO: SOME DISCUSSION ON P2P ARCHITECTURES
%
%\cite{matei_mapgnutella_2002, lv_randomwalks_2002, merugu_str2unstr_2003}
%showed that the ad-hoc network topology of unstructured overlay networks that
%preserve \emph{Power Law} and \emph{Small World} characteristics\footnote{Power
%Law describes the node degree while the Small World describes characteristics
%of path length and clustering coefficient. The clustering coefficient for a
%node $\upsilon$ in a graph $G = \left( V, E \right)$ is defined as the ratio of
%the existing connections between $\upsilon$'s neighbouring nodes to $\gamma
%\times \left( \gamma - 1 \right)$, where $\gamma$ is the number of neighbouring
%nodes of $\upsilon$. High cluster coefficient means that neighbouring nodes of
%any node $\upsilon$ likely connect one another.} \cite{faloutsos_powerlaw_1999,
%saroiu_measurefileshare_2002} offer a more promising approach. Particularly:
%\begin{itemize}
%  \item Peer-to-peer clients are extremely \emph{transient}. Unstructured
%systems can have high maintenance traffic in delivering messages, updating the
%mapping, discovering failures and replicating lost data or pointers, making
%them insufficient on highly volatile networks.
%  \item \emph{Keyword searches} versus \emph{exact-match queries}. In DHTs
%there is a tight control between the data placement and the topology of the
%network. For this reason it is hard to efficiently support partially matched
%queries while Gnutella and other similar systems effortlessly support keyword
%searches and other complex queries since the mechanism is realized locally, on
%a node-by-node basis.
%  \item Popular content is located at multiple peers and thus it is more likely
%for a flooding-based search to return results. DHTs, on the other hand, fit
%better in the systems which require ability to reliably locate content, even in
%the extreme case that only a single-copy exists in the network.
%\end{itemize}

@@

Ideally, an overlay network should be constructed to achieve an optimal 
mapping among the overlay paths and the underlying IP network links to avoid
inefficient states. The problem of constructing an optimal overlay is referred
to as the \emph{topology mismatch problem}, and is formally defined as follows:
\begin{definition}
Let $V = \{v_1, ..., v_n\}$ be a set of points denoting the network nodes,
$\{v_i, v_j\} \in E$ be the set of unicast distances between nodes $v_i$ and
$v_j$, $G=(V,E)$ be a complete distance graph over $V$. The topology mismatch
problem is to construct a minimal spanning tree, where node degree is
restricted to a constant ($k\geq 2$) by the bandwidth of each node $v_i$.
\end{definition}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Motivation and Goal for this Survey}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
A topology unaware overlay network is able to control the sequence of peers a
message traverses before reaching its destination, but it is completely unaware
of how the actual packets are switched at the underlying infrastructure along
the overlay path. For example, a single logical point-to-point link on the
overlay typically corresponds to multiple physical links in the
underlying layer. Additionally, a link in the underlying network often lies
on several overlay paths causing increase of the traffic on the
link, known as the link's \emph{stress}~\cite{CRSZ2002}. Even in the case
of an approach that provides mechanisms to a newcoming node to detect close-by
peers at join time, the stochastic behaviour with which peers join and leave
the overlay network, called the network's churn, further undermines the effort
for maintaing the best position in the network throughout the life-time of a
peer.

The topology mismatch problem is exacerbated by the extremely large amounts of
traffic generated by highly popular P2P applications (refer to the discussion
made in Section~\ref{section:intro}). Thus, solving the topology mismatch
problem is a fundamental challenge in contributing to the overall efficiency of
the Internet. Unfortunately, topology mismatch is known to be an NP-Hard problem
\cite{NPBOOK,chawathe_scattercast_2000}. Adding to the complexity of the problem
is the fact that end-to-end latencies demonstrate \emph{triangle inequality
violations (TIVs)} which are a consequence of the Internet's structure and
routing policies and thus will remain a property of the Internet for the
foreseeable future \cite{zheng_irprtt_2005}. TIVs affect both network coordinate
\cite{cox_vivaldi_2004,wong_meridian_2005} and positioning \cite{ng_gnp_2001}
systems and makes the construction of IP-topology-aware overlays difficult.

Over the past several years, researchers have proposed and studied an extensive
array of heuristic solutions to the topology mismatch problem. The purpose of
this survey is to gather and organize the extensive knowledge that has been
produced. We hope to assist the reader to understand the different approaches
that have been proposed to tackle the topology mismatch problem. In order to do
so, we dedicate a discussion subsection after the presentation of the algorithms
for both unstructred and structured architectures. This section offers:
\begin{inparaenum}[\itshape i\upshape)]
  \item further discussion that can help the reader identify, through
a taxonomy, the pluses and minuses in the preceeding material,
  \item a comprehensive tabular organisation of the key-point information, and
  \item an attempt to give a pictorial comparison of the relative performance of
the algorithms.
\end{inparaenum}

In discussion we offer the reader a deeper insight for the observations that
pushed research toward some direction. Thus, we try to categorise these
approaches so that we can organise directions making them comprehensible
and helping the reader build critical thinking on the advantages and
disadvantages of each approach.

@@

Pictorial comparison consists of bar charts that give a relative feeling of the
perfomance of the various algorithms, discussed in the corresponding section, in
terms of \emph{efficiency}, \emph{overhead} and \emph{scalability}; three
important characteristics for every distributed algorithm. For all we used a
coarse grained, three level, gradation to denote how well the algorithms do,
namely \emph{low}, \emph{medium} and \emph{high}. Each category has its own
interpretation of the above literal values. Efficiency means how well the
algorithm performs its search and topology adaptation functions, without
effecting other characteristics of the networks (e.g. BitTorrent's optimal
dowload performace). To name few, we assume that efficieny is
negatively effected when an algorithm reduces the search scope. Moreover, the
minimum-spanning-tree-based tecniques have slow convergence speed in topology
adaptation or the high clustering impacts load balancing and constrains search
scope (or at least increases search satisfaction time), all reducing overall
efficiency. With overhead we track the cost to compute and communicate peer
join, message forwarding and topology maintenance. For example when exchanging
cost tables only along neighbours the traffic generated can be considered
trivial. Also duplicates minimisation is a plus and lazy or heart-beat-based
overlay control mechanisms impose different amount of stress to the network.
Nevertheless, caching/replication helps reducing the averall overhead by
constraining the query from spreading too much. Minimum-spanning-tree-based
approaches's low convergence speed we mentioned above for efficiency means
additional computational and communicational overhead. % TODO: We check
% complexity in the asymptotic sence, using \emph{Big O} notation % in order to
% check how the algorithm responds t. We take into account topology % creation and
% topology maintenance...
% TODO: HELP NEEDED!
With scalability we check the systems behaviour with respect to the number of
participating peers. Low, medium and high scalability can be generally
considered in the order of hundrends, tenths of thousands and millions,
respectivelly. Fully distributed aproaches is a plus (no system-centric entities
involved, no need for global knowledge) and topology adaptation streanghtens
scalability in highly dynamic environments. Reduced search scope, on the other
side, penaltises the scalability since the more peers comming in the network the
more potentially unsatisfied queries there will be. Furthermore, clock
synchonisation is a limiting factor to scalability of a distributed systems.
Again to name a few.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Peer-to-Peer (P2P) Overlay Architectures}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Circa 2000, the first P2P file-sharing systems introduced the \emph{servent}
concept \cite{gnutella}, a \emph{portmanteau} that blends the notions of server
and client to denote the twofold role of a node participating in the P2P
network. Such server-less systems have proven to be able to achieve outstanding
aggregate resource capacities as more and more participants join the system
without requiring additional expenditure for infrastructure. While certain
undesirable features such as 
free-riding~\cite{saroiu_measurefileshare_2002,adar_gnutellafreeriders_2000,hughes_gnutellafreeride_2005},
the distribution of illegal content and other \emph{socio-technical}
issues \cite{hughes_socp2p_2008}, have arisen, peer-to-peer systems have
continued to gain popularity mainly because they have successfully supported
popular applications (i.e. file-sharing) amongst vast numbers of participating
users.

@@

Designers of \emph{centralized} architectures (see
Figure~\ref{figure:p2p-archs:centralized}) were the first to recognize that
requests for resources (e.g. CPU cycles or popular content) need not be sent to
a dedicated server but instead could be handled by the many hosts that already
posses the resources. The downside of this approach is that it requires a
centralized searching facility which becomes a single point of failure, a
scalability bottleneck, and a target of malicious attacks (e.g.,
\emph{Denial-of-Service (DoS) attacks}).

The most successful incarnation of the centralized approach is the file-sharing
application \emph{Napster}\cite{napster}. Napster maintained a \emph{central
index server} based on file lists provided by participating peers. The central
index server was queried by users and it returned pointers to the actual
content. Thus, by centralizing search while distributing downloads,  Napster
achieved a highly functional design that, at its height, attrated 26 million
users sharing approximately 80 million songs\cite{jmm_naptopusage_2001}.
Napter's  centralized nature was what ultimately brought it down after Recording
Industry Association of America (RIAA) filed a lawsuit for copyright infringemnt
of the intellectual property of artists whose music was distributed by the
Napster application. RIAA was able to point to the centralized indexing
component of Napster as the entity resposible for illegal song-trading.

The centralized approach was quickly replaced by architectures that distribute
both search and resource provision capabilities (see
Figure~\ref{figure:p2p-archs:unstructured-full}). In these \emph{decentralized}
architectures, resource placement within the overlay topology is
random~\cite{YG-M2002}. For this reason they are referred to as
\emph{unstructured}. The most important properties of such systems are that they
support inherent heterogeneity of peers, are highly resilient to peer failures,
and incur low maintenance overhead at handling the dynamics of peer
participation \cite{stutzbach_churn_2006}. In the literature, they are also
known as \emph{broadcast-based} systems, because they use message flooding among
peers to propagate search queries. A well-known example of the fully
decentralized
unstructured approach is Gnutella, in its first realization (v.0.4)
\cite{gnutellav04}.

A key disadvantage of the unstructured approach is that message flooding burdens
the network since queries travel within the network randomly, visiting nodes
that do not have the resource of interest and thus wasting bandwidth.  To save
on bandwidth, unstructured networks typically limit how long a query travels
within the overlay (via a time-to-live (TTL) parameter). When a query is
received by a node, it decreases the TTL by one unit. If the TTL has not reached
zero, the node forwards the query to its neighbors.  Otherwise, it drops the
query. While this approach prevents queries from visiting the entire network, it
does not guarantee that the resource of interest, (e.g., a rare recording 
of a musical group from the 1930s) will be found.

@@

To fully address the disadvantages of decentralized unstructured approaches,
\emph{decentralized structured} schemes have been proposed (see
Figure~\ref{figure:p2p-archs:structured}). The key goal of these systems is to
provide a self-organizing infrastructure for large-scale P2P applications
\cite{ratnasamy_can_2001,stoica_chord_2001,antony_pastry_2001,zhao_tapestry_2001,maymounkov_kademlia_2002,rgrk_bamboo_2004}.
They implement a \emph{Distributed Hash Table (DHT)} that maps objects to nodes
through a deterministic mechanism. The DHT provides a guaranteed bound on the
number of overlay routing hops that have to be taken to locate a resource, even
in the case when only a single copy exists in the system.  This means
$O \left( log n \right)$ hops, compared to unstructured networks that require
$O \left( n \right)$ to reliably locate any object. Unfortunately this
efficiency does not come without cost. Structured overlays can only support
exact-match queries (i.e., queries that identify resources by name) as opposed
to content-based retrieval provided by unstructured overlays. This means
that unstructured overlays can support more versatile resource location queries
such as keyword and partial matching searches. Several popular file-sharing
peer-to-peer applications have been based on DHTs including
Overnet/eDonkey~\cite{overnet}, Kademlia/Kad
Network~\cite{maymounkov_kademlia_2002}, some flavors of
BitTorrent~\cite{c_bittorrent_2003}, and many more.  Moreover, DHTs have sparked
a flurry of research activity and development for a large range of applications:
from distributed search engines to event notification infrastructures to
cloud-based platforms. We cite several examples in Section~\ref{section:intro}.

\begin{figure}[ht]
\centering
\subfigure[Centralized (SETI@Home or Napster). Peers query the centralized
entity (dotted lines) and then establish the connection to the data source.] {
  \includegraphics[scale=0.25]{img/pdf/centralized.pdf}
  \label{figure:p2p-archs:centralized}
}\qquad\qquad
\subfigure[Fully unstructured (Gnutella v.0.4). Data is distributed randomly,
the topology is also random and all participants are equal.] {
  \includegraphics[scale=0.25]{img/pdf/unstructured-full.pdf}
  \label{figure:p2p-archs:unstructured-full}
}\qquad\qquad
\subfigure[Hierarchical unstructured (Gnutella v.0.6 or FastTrack). Certain
peers (bigger circles) shoulder specific responsibilities (e.g., data
indexing).] {
  \includegraphics[scale=0.25]{img/pdf/unstructured-hierarchical.pdf}
  \label{figure:p2p-archs:unstructured-hierarchical}
}\qquad\qquad
\subfigure[Structured (Chord and Kademlia). Peers and data are placed into the
overlay in a deterministic manner.] {
  \includegraphics[scale=0.25]{img/pdf/structured.pdf}
  \label{figure:p2p-archs:structured}
}
\caption{The various peer-to-peer architectures.}
\label{figure:p2p-archs}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% TODO: SOME DISCUSSION ON P2P ARCHITECTURES
%
%\cite{matei_mapgnutella_2002, lv_randomwalks_2002, merugu_str2unstr_2003}
%showed that the ad-hoc network topology of unstructured overlay networks that
%preserve \emph{Power Law} and \emph{Small World} characteristics\footnote{Power
%Law describes the node degree while the Small World describes characteristics
%of path length and clustering coefficient. The clustering coefficient for a
%node $\upsilon$ in a graph $G = \left( V, E \right)$ is defined as the ratio of
%the existing connections between $\upsilon$'s neighboring nodes to $\gamma
%\times \left( \gamma - 1 \right)$, where $\gamma$ is the number of neighboring
%nodes of $\upsilon$. High cluster coefficient means that neighboring nodes of
%any node $\upsilon$ likely connect one another.} \cite{faloutsos_powerlaw_1999,
%saroiu_measurefileshare_2002} offer a more promising approach. Particularly:
%\begin{itemize}
%  \item Peer-to-peer clients are extremely \emph{transient}. Unstructured
%systems can have high maintenance traffic in delivering messages, updating the
%mapping, discovering failures and replicating lost data or pointers, making
%them insufficient on highly volatile networks.
%  \item \emph{Keyword searches} versus \emph{exact-match queries}. In DHTs
%there is a tight control between the data placement and the topology of the
%network. For this reason it is hard to efficiently support partially matched
%queries while Gnutella and other similar systems effortlessly support keyword
%searches and other complex queries since the mechanism is realized locally, on
%a node-by-node basis.
%  \item Popular content is located at multiple peers and thus it is more likely
%for a flooding-based search to return results. DHTs, on the other hand, fit
%better in the systems which require ability to reliably locate content, even in
%the extreme case that only a single-copy exists in the network.
%\end{itemize}

@@

Ideally, an overlay network should be constructed to achieve an optimal 
mapping among the overlay paths and the underlying network links to avoid
inefficient states were redundant physical resources are utilised for the
operation of a link on the overlay. The problem of constructing an optimal
overlay is referred to as the \emph{topology mismatch problem}, and is formally
defined as follows:
\begin{definition}
Let $V = \{v_1, ..., v_n\}$ be a set of points denoting the network nodes,
$\{v_i, v_j\} \in E$ be the set of unicast distances between nodes $v_i$ and
$v_j$, $G=(V,E)$ be a complete distance graph over $V$. The topology mismatch
problem is to construct a minimal spanning tree, where node degree is
restricted to a constant ($k\geq 2$) by the bandwidth of each node $v_i$.
\end{definition}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Motivation and Goal for this Survey}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
A topology unaware overlay network is able to control the sequence of peers a
message traverses before reaching its destination, but it is completely unaware
of how the actual packets are switched at the underlying infrastructure along
the overlay path. For example, a single logical point-to-point link on the
overlay typically corresponds to multiple physical links in the
underlying layer. Additionally, a link in the underlying network often lies
on several overlay paths causing increase of the traffic on the
link, known as the link's \emph{stress}~\cite{CRSZ2002}. Even in the case
of an approach that provides mechanisms to a new-coming node to detect close-by
peers at join time, the stochastic behavior with which peers join and leave
the overlay network, called the network's churn, further undermines the effort
for maintaining the best position in the network throughout the life-time of a
peer.

The topology mismatch problem is exacerbated by the extremely large amounts of
traffic generated by highly popular P2P applications (refer to the discussion
made in Section~\ref{section:intro}). Thus, solving the topology mismatch
problem is a fundamental challenge in contributing to the overall efficiency of
the Internet. Unfortunately, topology mismatch is known to be an NP-Hard problem
\cite{NPBOOK,C2000}. Adding to the complexity of the problem
is the fact that end-to-end latencies demonstrate \emph{triangle inequality
violations (TIVs)} which are a consequence of the Internet's structure and
routing policies and thus will remain a property of the Internet for the
foreseeable future \cite{zheng_irprtt_2005}. TIVs affect both network coordinate
\cite{cox_vivaldi_2004,wong_meridian_2005} and positioning \cite{ng_gnp_2001}
systems and makes the construction of IP-topology-aware overlays difficult.

Over the past several years, researchers have proposed and studied an extensive
array of heuristic solutions to the topology mismatch problem. The purpose of
this survey is to gather and organize the extensive knowledge that has been
produced. We hope to assist the reader to understand the different approaches
that have been proposed to tackle the topology mismatch problem. In order to do
so, we dedicate a discussion subsection after the presentation of the algorithms
for both unstructured and structured architectures. This section offers:
\begin{inparaenum}[\itshape i\upshape)]
  \item further discussion that can help the reader identify, through
a taxonomy, the pluses and minuses in the preceding material,
  \item a comprehensive tabular organization of the key-point information, and
  \item an attempt to give a pictorial comparison of the relative performance of
the algorithms.
\end{inparaenum}

In discussion we offer the reader a deeper insight for the observations that
pushed research toward some direction. Thus, we try to categorize these
approaches so that we can organize directions making them comprehensible
and helping the reader build critical thinking on the advantages and
disadvantages of each approach.

@@

Pictorial comparison consists of bar charts that give a relative feeling of the
performance of the various algorithms, discussed in the corresponding section,
in
terms of \emph{efficiency}, \emph{overhead} and \emph{scalability}; three
important characteristics for every distributed algorithm. For all we used a
coarse grained, three level, gradation to denote how well the algorithms do,
namely \emph{low}, \emph{medium} and \emph{high}. Each category has its own
interpretation of the above literal values. Efficiency means how well the
algorithm performs its search and topology adaptation functions, without
effecting other characteristics of the networks (e.g. BitTorrent's optimal
download performance). To name few, we assume that efficiency is
negatively effected when an algorithm reduces the search scope. Moreover, the
minimum-spanning-tree-based techniques have slow convergence speed in topology
adaptation or the high clustering impacts load balancing and constrains search
scope (or at least increases search satisfaction time), all reducing overall
efficiency. With overhead we track the cost to compute and communicate peer
join, message forwarding and topology maintenance. For example when exchanging
cost tables only along neighbors the traffic generated can be considered
trivial. Also duplicates minimization is a plus and lazy or heart-beat-based
overlay control mechanisms impose different amount of stress to the network.
Nevertheless, caching/replication helps reducing the overall overhead by
constraining the query from spreading too much. Low convergence speed of
minimum-spanning-tree-based approaches, we mentioned above for efficiency,
results also in additional computational and communicational overhead.
% TODO: We check
% complexity in the asymptotic sense, using \emph{Big O} notation % in order to
% check how the algorithm responds t. We take into account topology % creation and
% topology maintenance...
% TODO: HELP NEEDED!
With scalability we check the systems behavior with respect to the number of
participating peers. Low, medium and high scalability can be generally
considered in the order of hundreds, tenths of thousands and millions,
respectively. Fully distributed approaches is a plus (no system-centric entities
involved, no need for global knowledge) and topology adaptation strengthens
scalability in highly dynamic environments. Reduced search scope, on the other
hand, penalizes the scalability since the more peers coming in the network the
more potentially unsatisfied queries will there be. Furthermore, clock
synchronization is a limiting factor to scalability of a distributed system.
